---
title: Platformization
---

{{< include /_includes/_data.qmd >}}




## Emojis and emotionalized text

Emoji usage in headlines and captions is considered a typical feature of news platformization, but overall, only **14%** of all posts contained emojis, and 187 outlets never used them. TikTok posts were more likely to include emojis than YouTube Shorts posts – on average, TikTok posts contained 11% more emojis. Emoji usage also varied significantly by outlet - with some outlets using emojis in over 80% of their posts - and country, with the highest rates observed in Switzerland, the Czech Republic, and Spain, and the lowest in India, Japan, and Taiwan. 


```{r}
#| cache: true

m1 = d |>
  mutate(n_emoji = emoji::emoji_detect(title) |> as.numeric()) |>
  glmer(n_emoji ~ 1 + (1|country), data = _, family = binomial)

m2 = d |>
  mutate(n_emoji = emoji::emoji_detect(title) |> as.numeric()) |>
  glmer(n_emoji ~ 1 + (1|country) + (1|outlet), data = _, family = binomial)

m3 = d |>
  mutate(n_emoji = emoji::emoji_detect(title) |> as.numeric()) |>
  glmer(n_emoji ~ platform + (platform|country), data = _, family = binomial)

country_preds = m1 |> avg_predictions(variables = "country") |> 
  as_tibble() |> 
  left_join(regions)


brand_preds = m2 |> avg_predictions(variables = "outlet") |> 
  left_join(distinct(d, outlet, country, region)) |> 
  as_tibble() |> 
  left_join(country_preds |> select(country, avg = estimate))
```


::: {.panel-tabset group="comparison"}

### Emoji use by platform

```{r}
#| fig-height: 2
avg_predictions(m3, variables = "platform", re.form = NA) |> 
  ggplot(aes(x = platform, y = estimate, ymin = conf.low, ymax = conf.high))+
  geom_pointrange()+
  coord_flip(ylim = c(0,.2))+
  scale_y_continuous(labels = scales::percent)+
  labs(x = "", y = "Share of posts with emojis", title = "Who uses emojis?", subtitle = "Share of posts containing emojis, by platform")
```



### Emoji use by country 

```{r}
#| fig-height: 10

brand_preds |> 
  left_join(regions) |> 
  ggplot(aes(x = reorder(country, avg),  y = estimate, color = region))+
  geom_point(alpha = .33, size = 1)+
  geom_pointrange(data =country_preds, aes(x = country, y = estimate, ymin = conf.low, ymax = conf.high, color = region))+
  #geom_point(data = country_preds, size = 5)+
#  geom_point(data = brand_preds, size = 1, alpha = .5) +
  coord_flip(ylim = c(0,1))+
  scale_y_continuous(labels = scales::percent)+
  #scale_color_manual(values = c("#ff0050", "#00aaaa"))+
  labs(x = "", y = "Share of posts with emojis", title = "Who uses emojis?", subtitle = "Proportion of posts containing emojis, by country", color = "Region")
```

:::
