---
title: Platformization
bibliography: references.bib
---

{{< include /_includes/common.qmd >}} 

## Video and text features

```{r vid_analysis}
#| include: false
vid_results = read_data("is_vertical") |> 
  prep_for_analysis(d) |>  
  std_analysis("is_vertical", family = binomial())

vid_text = std_text(vid_results, title = "Video format", ylab = "Share of native vertical videos")
```

`r knitr::knit(text = std_plots(results = "vid_results",  title = "Video format", ylab = "Share of native vertical videos", text = vid_text))`

::: {.callout-note appearance="simple" collapse="true"}
## Result tables for video format

```{r}
#| results: asis
results_to_md(vid_results)
```
:::



```{r emo_analysis}
#| include: false
emo_results = d_analysis |> 
  mutate(emoji = emoji::emoji_detect(title)) |> 
  std_analysis("emoji", family = binomial())

emo_text = std_text(emo_results, ylab = "Share of posts with emojis", title = "Emoji use")
```

`r knitr::knit(text = std_plots(results = "emo_results",  ylab = "Share of posts with emojis", title = "Emoji use", text = emo_text))`

::: {.callout-note appearance="simple" collapse="true"}
## Result tables for emoji use

```{r}
#| results: asis
results_to_md(emo_results)
```
:::


## Audience interactions

```{r you_analysis}
#| include: false

you_results = read_data("interactions_new") |> 
  prep_for_analysis(d) |>
  mutate(you = direct_audience_address) |> 
  #mutate(you = str_detect(tolower(title), "\\b(you|your|yours)\\b") |> as.numeric()) |> 
  std_analysis("you", family = binomial)

you_text = std_text(you_results, ylab = "Share of posts addressing the audience")
```

`r knitr::knit(text = std_plots(results = "you_results",  ylab = "Share of posts addressing the audience", title = "Addressing the audience", text = you_text))`

::: {.callout-note appearance="simple" collapse="true"}
## Result tables for addressing the audience

```{r}
#| results: asis
results_to_md(you_results)
```
:::



```{r inter_analysis}
#| include: false

inter_results = read_data("interactions_new") |> 
  mutate(inter = if_any(starts_with("call"), ~ . == TRUE))|> 
  prep_for_analysis(d)  |> 
  std_analysis("inter", family = binomial)
inter_text = std_text(inter_results, ylab = "Share of posts calling for audience interactions such as liking, sharing or commenting, or visiting a website etc.")
```

`r knitr::knit(text = std_plots(results = "inter_results",  ylab = "Share of posts calling for audience interactions", title = "Interaction calls", text = inter_text))`

::: {.callout-note appearance="simple" collapse="true"}
## Result tables for interaction calls

```{r}
#| results: asis
results_to_md(inter_results)
```
:::

## Measures

Video format was coded using zero-shot classification with multimodal LLMs using video frames. Emoji use was measured using the `emo_detect()` function from the **{emoji}** package [@emoji]. Audience interactions were coded using zero-shot classification with multimodal LLMs using post text, transcript and video frames.

```{r}
#video_rel = read_data("vert")|> 
#  distinct(id, model, .keep_all = T) 
inter_rel = read_data("interactions_new")|> 
  distinct(id, model, .keep_all = T) 
d_rel = inter_rel
codebook = get_codebook("interactions_new")
```


{{< include /_includes/_rel.qmd >}} 
