---
title: Platformization
---

{{< include /_includes/_data.qmd >}}


*Platformization* describes the growing trend of news being produced and distributed through – and increasingly by – digital platforms like Instagram, YouTube, and TikTok. This process fundamentally alters news production, prioritizing algorithmic engagement over traditional journalistic norms. Consequently, news are assumed to be more visually-driven, emotionalized, and personalized, often delivered by non-traditional actors. 


## Titles, captions and other text


```{r}
m1 = d |>
  mutate(n_emoji = emoji::emoji_detect(title) |> as.numeric()) |>
  glmer(n_emoji ~ 1 + (1|country), data = _, family = binomial)

m2 = d |>
  mutate(n_emoji = emoji::emoji_detect(title) |> as.numeric()) |>
  glmer(n_emoji ~ 1 + (1|country) + (1|outlet), data = _, family = binomial)

country_preds = m1 |> avg_predictions(variables = "country") |> 
  as_tibble() |> 
  left_join(regions)
```


```{r}
#| fig-height: 10


brand_preds = m2 |> avg_predictions(variables = "outlet") |> 
  left_join(distinct(d, outlet, country, region)) |> 
  as_tibble() |> 
  left_join(country_preds |> select(country, avg = estimate))


brand_preds |> 
  left_join(regions) |> 
  ggplot(aes(x = reorder(country, avg),  y = estimate, color = region))+
  geom_point(alpha = .33, size = 1)+
  geom_pointrange(data =country_preds, aes(x = country, y = estimate, ymin = conf.low, ymax = conf.high, color = region))+
  #geom_point(data = country_preds, size = 5)+
#  geom_point(data = brand_preds, size = 1, alpha = .5) +
  coord_flip(ylim = c(0,1))+
  scale_y_continuous(labels = scales::percent)+
  #scale_color_manual(values = c("#ff0050", "#00aaaa"))+
  labs(x = "", y = "Share of posts with emojis", title = "Who uses emojis?", subtitle = "Proportion of posts containing emojis, by country", color = "Region")
```


