---
index: true
---

{{< include /_includes/common.qmd >}} 

```{r, include = F}
country = params$country
d = d |> 
      filter(country == params$country) 


options(knitr.kable.NA = '-')

```


```{r}
n_posts = nrow(d)
n_outlets = n_distinct(d$brand)
n_days = n_distinct(as.Date(d$timestamp))
per_day = round(n_posts/n_days,0)
first_day = min(as.Date(d$timestamp))
last_day = max(as.Date(d$timestamp))

avg_per_day = d |> 
  count(platform, outlet) |> 
  group_by(platform) |> 
  summarise(Posts = round(median(n, na.rm = T)/n_days,1))
```

We collected data from **`r n_outlets` news outlets** on TikTok, Instagram and YouTube Shorts: <br/> `r outlet_desc(d)`. 

Overall, these outlets published  **`r n_posts` posts**. 

The median outlet published **`r filter(avg_per_day, platform =="TikTok")$Posts` TikToks**, **`r filter(avg_per_day, platform =="Instagram")$Posts` Instagram** reels, and **`r filter(avg_per_day, platform =="YouTube Shorts")$Posts` YouTube** shorts per day.

## Basics 

### Platforms shares

```{r platforms}
b = mean(d$brands_per_country)
d |> 
  group_by(Platform = platform) |> 
  summarise(n_outlets = n_distinct(brand), n = n()) |> 
  mutate(`% of brands` = n_outlets/b*100,
         `% of posts` = n/sum(n)*100) |> 
  mutate_if(is.numeric, round) |> 
  rename(`Active brands` = n_outlets, Posts = n)
```


### Published posts



```{r pubs}
dups = country_tab("is_dup", d = d) |> 
  mutate(is_dup = round(is_dup*100))

overall = d |> 
  count(platform, sort = T) |> 
  mutate(Posts = sum(n), outlet_type = "") |> 
  mutate(brand = paste(fa("globe"), "Overall"))

tab = d |> 
  count(brand, platform, outlet_type, sort = T) |> 
  group_by(brand) |> 
  mutate(Posts = sum(n)) |> 
  ungroup() |> 
  rbind(overall) |> 
  spread(platform, n, fill = 0) |> 
  with_fa() |> 
  select(-outlet_type) |> 
  slice(2:n(), 1) |> 
  select(Outlet = brand, Posts, TikTok, Instagram, `YouTube Shorts`)  |> 
  left_join(dups) |> 
  rename(`Content duplication (%)` = is_dup)


tab |> 
  to_kable()
```
## Outlet analyses 

### Platformization


```{r platformization}
c("duration", "is_vertical", "you", "inter") |> 
  map(country_tab,  d = d) |> 
  reduce(left_join) |> 
  mutate_at(vars(is_vertical:inter), ~ .*100) |> 
  mutate_if(is.numeric, round) |> 
  rename(`Video duration (sec)` = duration,
         `Vertical videos (%)` = is_vertical,
         `Addressing the audience (%)` = you,
         `Calling for interactions (%)` = inter) |> 
  to_kable()
```
### Diversity



```{r diversity}
c("prop_fem", "m_age", "iqr_age", "topic_div") |> 
  map(country_tab,  d = d) |> 
  reduce(left_join) |> 
  mutate(prop_fem = prop_fem*100) |> 
  mutate_if(is.numeric, round) |> 
  rename(`Visible women (%)` = prop_fem,
         `Mean age` = m_age,
         `Age diversity (IQR)` = iqr_age,
         `Topic diversity (topics)` = topic_div) |> 
  to_kable()
```


**Note:** Outlet-level results are empirical Bayes estimates from the respective analyses.